---
title: "TP-Projet"
author: "ZHONG"
output:
  html_document: default
  pdf_document: default
---

### Research questions
i.   Which state has the highest proportion of never/daily/weekly/monthly Pop drinkers?
ii.  if the frequency of drinking Pop causes more harm to people.
iii. Average never/daily/weekly/monthly POP drinkers' weight.


### For this question we will be using the variables :
ssbsugar: How Often Do You Drink Regular Soda Or Pop? 

_state: State Fips Code

physhlth: Number Of Days Physical Health Not Good

weight2: Reported Weight In Pounds

### Load packages and data
```{r get_the_data}
load("brfss2013.Rdata")
dim(brfss2013)
```

```{r load_libraries, message=FALSE}
library(dplyr)
library(ggplot2)
```

```{r eval=FALSE}
PopDrinker <- select(brfss2013, X_state, ssbsugar, physhlth, weight2) %>% 
  filter(!is.na(X_state), !is.na(ssbsugar), !is.na(physhlth), !is.na(weight2), X_state !="Michigan")

```

### Question 1

```{r eval=FALSE}
StateDrinker <- select(PopDrinker, X_state, ssbsugar) %>%
  group_by(X_state) %>%
  summarise(n = n())

StateNeverDrinker <- select(PopDrinker, X_state, ssbsugar) %>%
  filter(ssbsugar==0) %>%
  group_by(X_state) %>%
  summarise(n = n())

StateDailyDrinker <- select(PopDrinker, X_state, ssbsugar) %>%
  filter(ssbsugar>100, ssbsugar<200) %>%
  group_by(X_state) %>%
  summarise(n = n())

StateWeeklyDrinker <- select(PopDrinker, X_state, ssbsugar) %>%
  filter(ssbsugar>=200, ssbsugar<300) %>%
  group_by(X_state) %>%
  summarise(n = n())

StateMonthlyDrinker <- select(PopDrinker, X_state, ssbsugar) %>%
  filter(ssbsugar>=300, ssbsugar<400) %>%
  group_by(X_state) %>%
  summarise(n = n())

```
plot the proportion of daily Pop drinkers in each state
```{r eval=FALSE}
ggplot(StateDailyDrinker, aes(x = X_state, y = StateDailyDrinker$n / StateDrinker$n)) +
    geom_bar(stat = "identity", width = 0.5) + 
    labs(x = "states", y = "proportion", title = "proportion of daily Pop drinkers")+
    theme(axis.text.x = element_text(angle=90, hjust=1, vjust=.5))

```
plot the proportion of never/daily/weekly/monthly Pop drinkers in each state
```{r eval=FALSE}
states <- rep(StateDrinker$X_state, each = 4)
frequency <- rep(c("never", "daily", "weekly", "monthly"), times = 15)
propor <- c(1:60)
for (i in 0:14){  
  propor[4*i +1] <- StateNeverDrinker$n[i+1]/StateDrinker$n[i+1]
  propor[4*i +2] <- StateDailyDrinker$n[i+1]/StateDrinker$n[i+1]
  propor[4*i +3] <- StateWeeklyDrinker$n[i+1]/StateDrinker$n[i+1]
  propor[4*i +4] <- StateMonthlyDrinker$n[i+1]/StateDrinker$n[i+1]
}  
ggplot(data = data.frame(states, frequency, propor), mapping = aes(x = factor(states), y = propor, fill = frequency)) + 
    geom_bar(stat = 'identity', position = 'dodge') + 
    labs(x = "states", y = "proportion", title = "proportion of Pop drinkers")+
    theme(axis.text.x = element_text(angle=90, hjust=1, vjust=.5))
```



